\documentclass[main.tex]{subfiles}

\onlyinsubfile{\input{preamble}}     

\onlyinsubfile{\usepackage{xr}}
% https://www.overleaf.com/learn/how-to/Cross_referencing_with_the_xr_package_in_Overleaf

\onlyinsubfile{     
 \geometry{
   reset,
   a4paper,
   textwidth=5cm,textheight=5cm,
   % exact values will vary by template
   paperwidth=453pt+0.8cm,
   paperheight=706pt+2cm, 
   % above values found using \usepackage{printlen} \printlength\textwidth \printlength\textheight https://tex.stackexchange.com/questions/39383/determine-text-width
   text={453pt,706pt}, % without this line, errors occur
   %marginparwidth = 2cm,
   marginparsep = -2.5cm
 }
} 

\begin{document}
 
\section{Problem 641}

\begin{mdframed}[backgroundcolor = lightgray!10]
Consider a row of $n$ dice all showing $1$.

First turn every second die, $(2, 4, 6, \dots)$, so that the number showing is increased by $1$. Then turn every third die. The sixth die will now show a $3$. Then turn every fourth die and so on until every $n$'th die (only the last die) is turned. If the die to be turned is showing a 6 then it is changed to show a 1.

Let $f(n)$ be the number of dice that are showing a $1$ when the process finishes. You are given $f(100) = 2$ and $f(10^8) = 69$.


Find $f(10^{36})$.
\end{mdframed}

Upon inspection, one sees that the problem is asking us to compute
%
\begin{align}
 \# \{ k \in \{1, \dots, n \} \mid
 \sigma(k) \text{ mod } 6 = 1\},
\end{align}
%
where $\sigma: \mathbb N \to \mathbb N$ is the function that counts how many divisors a given integer has, e.g. $\sigma(12) = 6$ and $\sigma(p) = 2$, where $p$ is a prime number. 

In words, we are tasked to find numbers satisfying 
%
\begin{align}
 \sigma(k) = 1, 7, 13, 19, \dots
\end{align}

Since the above numbers are all odd, we may search through the squares:
%
\begin{align}
 \# \{ k = \widetilde k^2 \in \{1, \dots, n \} \mid
 \sigma(k) \text{ mod } 6 = 1\},
\end{align}
%
A quick and brute-force approach easily yields the results given in the table below. 

Upon inspecting the table, we see that the $n$ of interest has representation
%
\begin{align}
 n = a^6 b^4,
 \qquad b = \prod_{i=1}^{2m} p_i,
 \qquad a \in \mathbb N,
 \qquad m \in \mathbb N,
 \qquad p_i\text{'s are distinct is primes}.
\end{align}
%
Most of the values in the table fit the representation above. A few needs to adjusted slightly, e.g. $n = 85525504 = 2^{10} \cdot 17^4 = 2^6 \cdot (2 \cdot 17)^4$. Note that the numbers whose prime factorization contains an even number of distinct primes are those numbers whose M\"{o}bius value is equal to one. 

For each value of $b$, there are
%
\begin{align}
 \frac{n^{1/4}}{b^{3/2}}
\end{align}
%
choices for $a$, because $a^6 b^4 \leq n$ must hold. If we set $b=n^{\frac{1}{6}}$ in the above, then we get $1$.

Let $\mu: \mathbb N \to \{-1, 0, 1\}$ be the M\"{o}bius function and let $M_+: \mathbb R_+ \to \mathbb N$, given by
%
\begin{align}
 M_+(x) := \sum_{i=1}^{\lfloor x \rfloor} \mu^2(i),
\end{align}
%
be the function that counts the natural numbers $i \leq \lfloor x \rfloor$ such that $\mu(i) = 1$.

Then
%
\begin{align}
 f(n)
 =
 \sum_{a = 1}^{n^{1/6}}
 M_+ \left(
 \frac{n^{1/4}}{a^{3/2}}
 \right).
\end{align}
%
The values of M\"{o}bius function can easily be computed using a sieve (the Sieve of Eratosthenes works fine), and the rest is trivial. 

\input{641_table.tex}                

\end{document}
